### 2020-07-21 paper/conclusion.tex
After Andrei's review

\section{Conclusion} \label{Conclusion}
In the current work, we proposed a reactivity control system design for the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for the full-core geometry using the
SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions:
(1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and TRU, extracted from \gls{LWR} \gls{SNF}.

@@

In case of malfunction of the other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD failed to counteract the excess 
reactivity of the core initially loaded with reactor-grade Pu and TRU elements.
However, the worth of the outer ring of the CSD is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U.

@@

\section{Future work}
The authors intend to evaluate the effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine and 
batch-wise tool SaltProc \cite{rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
simulation which takes into account the neutron precursors drift.

>>>>

\section{Conclusion} \label{Conclusion}

The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs. However, we cannot rely on online reprocessing to adjust reactivity quickly. Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods. Consequently, we proposed a reactivity control system design based on control rods in addition to the 
online feed system reactivity control in the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for a full 3D model of the SD-TMSR using the
SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions:
(1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and TRU, extracted from \gls{LWR} \gls{SNF}.

@@

In case of malfunction of the other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD failed to counteract the excess 
reactivity of the core initially loaded with reactor-grade Pu and TRU elements. Therefore, the fuel salt must be drained into subcritical tanks to shut down the SD-TMSR.
However, the worth of the outer ring of the CSD is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U.

@@

\section{Future work}
The authors intend to evaluate the effect of the fuel salt 
depletion on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018}. Additionally, the authors intend to investigate
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
simulation which takes into account the neutron precursors drift.

### 2020-07-21 paper/cover-letter/cover-letter.tex
After Andrei's review

		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, and Prof. Kathryn D. Huff) are submitting for exclusive consideration of publication as a research article in Annals of Nuclear Energy. The current manuscript introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR. This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state.

		Notably, this paper in its initial form has been rejected from Progress of Nuclear Energy journal. However, we have addressed the major concerns of the reviewers. It is our belief that the manuscript is substantially improved after implementing the suggested comments and edits.

>>>>

		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Dr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, and Prof. Kathryn D. Huff) are submitting for exclusive consideration of publication as a research article in Annals of Nuclear Energy. The current manuscript introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR. This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state.

		I want to inform you that this manuscript in its initial form has been rejected by Progress of Nuclear Energy journal. However, we have addressed the major concerns of the reviewers. It is our belief that the manuscript is substantially improved after implementing the suggested comments and edits.

### 2020-07-21 paper/introduction.tex
After Andrei's comments
Cover letter and minor changes
After addressed some comments from #16
After Andrei's review

At the Beginning of Life (BOL), MSRs are commonly loaded with more
fuel than that required to achieve criticality (necessary for long-term core 
operation); this leads to excess reactivity at the BOL. Robertson (1971) assumed small excess reactivity for \gls{MSBR} loaded by $^{233}$U/$^{232}$Th fuel, thus only 2 control (graphite) rods for adjusting reactivity and 2 safety (B$_4$C) rods for emergency shutdown were suggested \cite{robertson_conceptual_1971}. However, scientists are concerned about $^{233}$U supply, since it does not exist anywhere. Our recently published paper \cite{ashraf2020Strategies} concluded that for realistic fueling scenarios (e.g., TRU/$^{232}$Th and Pu/$^{232}$Th), large excess reactivity is required. Betzler \emph{et al.} (2017) also reported large excess reactivity to operate Transatomic Power Molten Salt Reactor (TAP MSR) for a long time \cite{betzler2017assessment}. Additionally, Rykhlevskii \emph{et al.} (2019) studied the fuel cycle performance for various designs of the \gls{MSFR}. For MSFRs, a considerable excess reactivity is also required for long-term core operation \cite{rykhlevskii_fuel_2019}. Recent studies on MSRs showed that the excess reactivity 
at the BOL may vary from 1.2 \% for $^{233}$U-loaded core \cite{rykhlevskii2019modeling,betzler2016modeling} to 8.1 \% for Pu/TRU-loaded core \cite{ashraf2020Strategies}.

The online reprocessing and refueling system is designed to operate as long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}. However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its clones. Consequently, we need a prompt reactivity control system for emergencies. The most common and reliable procedure to control the reactor is to insert or withdraw control rods made of material with a large neutron absorption cross section (e.g., boron).
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency. Therefore, we should estimate 
the reactivity worth of the control rods.
The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{atkinson2019small}. Additionally, Nuclear Regulatory Commission (NRC) regulation requires that one of the reactivity control systems use control rods \cite{nuclear1987standard}.

@@

The online reprocessing and refueling is a distinguishing feature for MSRs comparing with traditional solid fuel reactors. Its neutron characters including $k_{eff}$, excess reactivity, Breeding Ratio (BR), and $^{233}$U production are totally different when operating from those of startup. The $k_{eff}$, excess reactivity, and neutron flux are all related to the scheme of reprocessing. Therefore, the worth of the control rods should be corresponding to the reprocessing scheme; that is, the rate of extraction and addition of elements. However, the present work focuses on the steady state calculations (i.e. without burnup).

All calculations presented in this work are performed using Monte-Carlo code SERPENT-2 version 2.1.31 \cite{leppanen2014serpent}.

>>>>

At the Beginning of Life (BOL), MSRs are commonly loaded with more
fuel than that required to achieve criticality (necessary for long-term core 
operation); this leads to excess reactivity at the BOL. Robertson \emph{et al.} analyzed the \gls{MSBR} loaded by $^{233}$U/$^{232}$Th fuel and concluded that two graphite rods are sufficient for adjusting reactivity during operation due to a small reactivity swing. Robertson \emph{et al.} also reported that 2 safety rods made of boron carbide (B$_4$C) are enough to safely shut the \gls{MSBR} down from any state \cite{robertson_conceptual_1971}. However, the $^{233}$U supply for commercial power plants is not readily available. Our recently published paper \cite{ashraf2020Strategies} concluded that for realistic fueling scenarios (e.g., enriched U/$^{232}$Th, TRU/$^{232}$Th and Pu/$^{232}$Th), large excess reactivity is required. Betzler \emph{et al.} also reported large excess reactivity in Transatomic Power Molten Salt Reactor (TAP MSR) to ensure a 30-year operation cycle \cite{betzler2017assessment}. Additionally, Rykhlevskii \emph{et al.} studied the fuel cycle performance for various Fast-Spectrum \gls{MSR} designs. For a fast MSRs, a considerable excess reactivity is also required for long-term core operation \cite{rykhlevskii_fuel_2019}. Recent studies on MSRs showed that the excess reactivity 
at the BOL may vary from 1.2\% for $^{233}$U-loaded core \cite{rykhlevskii2019modeling,betzler2016modeling} to 8.1\% for Pu/TRU-loaded core \cite{ashraf2020Strategies}.

The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs \cite{ashraf2019modeling,ashraf2019Preliminary}. However, we cannot rely on online reprocessing to adjust reactivity quickly, because loop time (time needed for one particle to make one full circulation through the primary loop) is approximately 20 seconds for MSBR and its analogs. Consequently, we need a prompt reactivity control system for emergencies. The most common and reliable way to control the reactivity is to insert or withdraw control rods made of a material with a large neutron absorption cross section (e.g., boron).
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency. Therefore, we should estimate 
the reactivity worth of the control rods.
The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{vcerba2017optimization}. 
The control rod worth and its efficiency in compensating excess reactivity is a subject of significant interest since it directly affects reactor safety \cite{atkinson2019small}. Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods (Criterion 26) \cite{nuclear1987standard}.

@@

The online reprocessing and refueling is a distinguishing feature for MSRs comparing with traditional solid fuel reactors. Its neutron characters including $k_{eff}$, excess reactivity, Breeding Ratio (BR), and $^{233}$U production are totally different when operating from those at startup. The $k_{eff}$, excess reactivity, and neutron flux are all related to the scheme of reprocessing. Therefore, the worth of the control rods should be corresponding to the reprocessing scheme; that is, the rate of extraction and addition of elements. However, the present work focuses on the steady-state calculations without taking into account fuel salt depletion.

All calculations presented in this work are performed using Monte-Carlo code SERPENT-2 version 2.1.31 \cite{leppanen2014serpent}. Delayed neutron precursor drift was neglected in this study.

### 2020-07-21 paper/methods.tex
After Andrei's review

The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li_optimization_2018,li2015analysis}. Among them, the SD-TMSR is proposed in 2018 \cite{li_optimization_2018}, which is a graphite-moderated molten salt reactor with thermal power of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum. The negative temperature coefficient of reactivity is also achieved in the design of SD-TMSR. Figure~\ref{fig:ff} illustrates the quarter-core view of the 
SD-TMSR. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.
\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
		SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}
In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e., $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
We adopted the same graphite density reported in the original SD-TMSR paper \cite{li_optimization_2018}.
Just have one sentence state it somewhere.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

@@

\begin{table}
	\caption{The densities of the absorbing materials.}
	\vspace{0.05in}
	\begin{center}	
		\begin{tabular}{|l | r|}  %[!ht]
			%%	\begin{tabularx}{\textwidth}{l | r}
			\hline
			Absorbers & Density [g/cm$^3$]\\
			\hline
			B$_4$C   &  2.54 \\
			HfB$_2$   &  10.5 \\
			HfH$_{1.62}$  &  11.4 \\
			Gd$_2$O$_3$   &  7.04 \\
			Eu$_2$O$_3$  &  7.38 \\
			SiC   & 3.21 \\
			AIM1 cladding   & 7.987 \\
			\hline
			%	\end{tabularx}
		\end{tabular}
		\label{tab:table111}
	\end{center}
\end{table}

>>>>

The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li2015analysis}. Among them, the SD-TMSR is proposed in 2018 \cite{li_optimization_2018}, which is a graphite-moderated molten salt reactor with thermal power of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum. SD-TMSR also offers a negative and strong temperature coefficient of reactivity \cite{li_optimization_2018}. Figure~\ref{fig:ff} illustrates the quarter-core view of the
SD-TMSR. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.
\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
		SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}
In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e., $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
We adopted the same graphite density reported in the original SD-TMSR paper (2.3 g/cm$^3$) \cite{li_optimization_2018} to be consistent with results in the literature.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

@@

\begin{table}
	\caption{The densities of the absorbing materials.}
	\vspace{0.05in}
	\begin{center}	
		\begin{tabular}{l  r}  %[!ht]
			%%	\begin{tabularx}{\textwidth}{l | r}
			\hline
			Absorbers & Density [g/cm$^3$]\\
			\hline
			B$_4$C   &  2.54 \\
			HfB$_2$   &  10.5 \\
			HfH$_{1.62}$  &  11.4 \\
			Gd$_2$O$_3$   &  7.04 \\
			Eu$_2$O$_3$  &  7.38 \\
			SiC   & 3.21 \\
			AIM1 cladding   & 7.987 \\
			\hline
			%	\end{tabularx}
		\end{tabular}
		\label{tab:table111}
	\end{center}
\end{table}

### 2020-07-21 paper/results.tex
Cover letter and minor changes
After Andrei's review

@@

The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady state 
calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
The previously studied $^{233}$U case recorded the maximum reactivity
during 60 effective full-power years (EFPY) of reactor operation to be 
$4.27\pm0.01$ $\$$ (see Figure~\ref{fig:keff_25}).
The proposed reactivity control system must compensate such reactivity at startup and during burnup.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff_25.png}
	\vspace{-0.5in}
	\caption{Uncontrolled effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.} 
	\label{fig:keff_25}
\end{figure}

@@

The inner ring of the CSD is located in the central zone of the SD-TMSR core 
(Figure~\ref{fig:core_25}), in which the volume ratio between molten salt and 
graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
a worth almost equal to the worth of all other CRs together (SSD + CSD outer ring) regardless of 
the absorbing material type (see Table~\ref{tab:worth}). This happens because the absorption cross section
decreases with the energy of the incident neutron; for example, boron absorbs neutrons in the thermal spectrum much 
greater than in the fast spectrum. Additionally, the maximum neutron flux is located in the central zone of the SD-TMSR (see Figure~\ref{fig:totalflux}); therefore the inner ring of the CSD has a worth higher than the worth of the outer ring of the CSD.

In case of malfunction of other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD will be able to compensate the excess reactivity of the core initially loaded by $^{233}$U.
Meanwhile, it will fail to compensate the excess 
reactivity of the core initially loaded by reactor-grade Pu and TRU elements.

@@

Insertion of the CR affects the neutron flux distribution, which is 
the primary reason for the amplification of CRWs indicated in 
Table~\ref{tab:worth}. Figure~\ref{fig:totalflux} illustrates the radial 
neutron flux distribution at the mid-core level with different CR positions: 
(1) all CRs withdrawn, (2) all CRs inserted, (3) all CSD inserted, (4) all SSD 
inserted. We chose the B$_4$C-90 as the absorbing material because of its high 
absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
CRs deforms the radial flux shape in certain positions, i.e., around CRs.
This shifts the neutron flux from the core center towards the 
periphery. The maximum neutron flux shift occurs when all CRs are inserted 
into the core \cite{girardin2007control}.
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{totalflux.png}
	\vspace{-0.5in}
	\caption{Radial neutron flux distribution at the mid-core for different 
	CR positions (CRs made of B$_4$C-90).} 
	\label{fig:totalflux}
\end{figure}

@@

Figure~\ref{fig:CSD} shows the integral CRW for only Control Safety Devices (CSD) clusters with six 
different absorbing materials. The results show that all absorbing materials 
have almost the same integral rod worth in the upper half of the core 
($<250$ cm from the upper boundary of the core). Further insertion of the 
CRs demonstrates that the strongest absorber, B$_4$C-90 outperforms other materials.
Notably, all results are based on steady state calculations.

>>>>

The SERPENT-2 is used to obtain the presented results.
We use the ENDF-VII.0 cross section library for all calculations in the current work. The statistical error in $k_{eff}$ is $\leq$ $25$ $pcm$.
The initial calculation state of a full 3D model of the SD-TMSR is identified by normal operation 
conditions (see Table~\ref{tab:table1}) and fully withdrawn control rod 
clusters. 
To validate the proposed control rods 
system we adopted the same operation conditions (as in the initial calculation 
state) and changed the position of the control rod clusters along the $Z$ 
direction.
The obtained results including reactivity, control rod 
worth, and interference effects (shadowing effects) are discussed below.

@@

The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady-state 
calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
The previously studied $^{233}$U case \cite{ashraf2020Strategies} recorded the maximum reactivity
during 60 effective full-power years (EFPY) of reactor operation to be 
$4.27\pm0.01$ $\$$ (see Figure~\ref{fig:keff_25} at $\approx$ 8 EFPY).
The proposed reactivity control system must compensate such reactivity at startup and during burnup.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff_25.png}
	\vspace{-0.5in}
	\caption{Uncontrolled effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.} 
	\label{fig:keff_25}
\end{figure}

@@

The inner ring of the CSD is located in the central zone of the SD-TMSR core 
(Figure~\ref{fig:core_25}), in which the volume ratio between molten salt and 
graphite is relatively small ($0.357$). Results show that the inner ring of the CSD has 
a worth almost equal to the worth of all other CRs together (SSD + CSD outer ring) regardless of 
the absorbing material type (see Table~\ref{tab:worth}). This happens because the absorption cross section
decreases with the energy of the incident neutron; for example, boron absorbs neutrons in the thermal spectrum much 
greater than in the fast spectrum. Additionally, the maximum neutron flux is located in the central zone of the SD-TMSR (see Figure~\ref{fig:totalflux}); therefore, the inner ring of the CSD has a worth higher than the worth of the outer ring of the CSD.

In case of malfunction of other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD will be able to compensate the excess reactivity of the core initially loaded by $^{233}$U.
Meanwhile, it will fail to compensate the excess 
reactivity of the core initially loaded by reactor-grade Pu and TRU elements. In this unlikely case, the fuel salt must be drained into subcritical tanks to shut down the SD-TMSR.

@@

Insertion of the CR affects the neutron flux distribution, which is 
the primary reason for the amplification of CRWs indicated in 
Table~\ref{tab:worth}. Figure~\ref{fig:totalflux} illustrates the radial 
neutron flux distribution at the mid-core level with different CR positions: 
(1) all CRs withdrawn, (2) all CRs inserted, (3) all CSD inserted, (4) all SSD 
inserted. We chose the B$_4$C-90 as the absorbing material because of its high 
absorption ability. As shown in Figure~\ref{fig:totalflux}, the insertion of 
CRs deforms the radial flux shape close to CRs.
This shifts the neutron flux from the core center towards the 
periphery. The maximum neutron flux shift occurs when all CRs are inserted 
into the core \cite{girardin2007control}.
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{totalflux.png}
	\vspace{-0.5in}
	\caption{Radial neutron flux distribution at the mid-core for different 
	CR positions (CRs made of B$_4$C-90).} 
	\label{fig:totalflux}
\end{figure}

@@

Figure~\ref{fig:CSD} shows the integral CRW for only Control Safety Devices (CSD) clusters with six 
different absorbing materials. The results show that all absorbing materials 
have almost the same integral rod worth in the upper half of the core 
($<250$ cm from the upper boundary of the core). Further insertion of the 
CRs demonstrates that the strongest absorber, B$_4$C-90 outperforms other materials.
Notably, all results are based on steady-state calculations.
